---
title: "DEA Write Up"
format: html
editor: visual
echo : false
---

Loading Relevant Libraries

```{r}

# Loading Librairies

library(tidyverse)
library(dplyr)
library(rio)
library(lubridate)


```

Adding Google Trends Data

```{r}

# Aggregating Google Tends data

trends_files <- list.files( path = "/Users/danielaina/Desktop/OMSBA R/Lab3_Rawdata",
                            pattern = "^trends_up_to.*\\.csv$",
                            full.names = TRUE)
google_trends_data <- bind_rows(lapply(trends_files, read_csv))


```

```{r}

google_trends_data <- google_trends_data %>%
  mutate(date_variable = ymd(str_sub(monthorweek, 1, 10)))
```

```{r}
google_trends_data <- google_trends_data %>%
  mutate(monthly_date = floor_date(date_variable, unit = 'month'))
```

```{r}
google_trends_data <- google_trends_data %>%
  group_by(schname, keynum) %>%
  mutate(std_index = (index - mean(index, na.rm = TRUE)) / sd(index, na.rm = TRUE)) %>%
  ungroup()

```

```{r}
aggregated_data <- google_trends_data %>%
  group_by(schname, monthly_date) %>%
  summarize(mean_std_index = mean(std_index, na.rm = TRUE))

head(aggregated_data)

```

Reading in scorecard data

```{r}

scorecard_data <- read_csv("/Users/danielaina/Desktop/OMSBA R/Lab3_Rawdata/Most+Recent+Cohorts+(Scorecard+Elements).csv")

```

Importing Id_name_data and cleaning for merger

```{r}

id_name_data <- import("/Users/danielaina/Desktop/OMSBA R/Lab3_Rawdata/id_name_link.csv")

```

```{r}

schools <- id_name_data %>%
  group_by(schname) %>%
  mutate(n = n())

```

```{r}

# Filter out schools that show up more than once
filtered_id_name_data <- schools %>%
  filter(n == 1) %>%
  select(schname, unitid, opeid)

final_data <- aggregated_data %>%
  inner_join(filtered_id_name_data, by = "schname") %>%
  inner_join(scorecard_data, by = c("unitid" = "UNITID", "opeid" = "OPEID")) %>%
  filter(PREDDEG == 3) %>% filter(monthly_date >= as.Date("2015-09-01")) %>%
  rename("median_earnings_" = "md_earn_wne_p10-REPORTED-EARNINGS")

# create the median income to set low and high value

threshold <- median(final_data$`median_earnings_`) # The median threshold income is 42,000


# Print the first few rows of the final data
head(final_data)

```

```{r}
# Regression Analysis for after scoore card relase showing low earning and high earning
library(fixest)

final_data$HighEarning <- ifelse(final_data$median_earnings_ >= threshold, 1, 0)
final_data$LowEarning <- ifelse(final_data$median_earnings_ <= threshold, 1, 0)


#create date value for date
release_date <- as.Date("2015-09-01")

```

Regression Portion

```{r}

#regression analysis

reg_model <- feols(log(mean_std_index) ~ HighEarning + LowEarning + monthly_date, data = final_data)

 etable(reg_model)
# Print model summary
summary(reg_model)


```

Graph

This graph shows the distribution of observations based on median earnings and mean standard index. this graph is separated by high earnings and low earnings

```{r}

ggplot(final_data, aes(x = median_earnings_ , y = mean_std_index, color = factor(HighEarning))) +
  geom_point() +  # scatter plot of observed data
  geom_smooth(method = "lm", se = FALSE, color = "blue") +  # fitted regression line
  labs(title = "Regression of mean_std_index on HighEarning",
       x = "Earnings",
       y = "mean_std_index")+
  scale_color_manual(values = c("red", "blue"),labels = c("Low Earnings", "High Earnings")) +
  theme_minimal()


```

The question of this project was among colleges that predominantly grant bachelor's degrees, did the release of the Scorecard shift student interest to high- earnings colleges relative to low- earning ones?

Notes about the data used:

-   my data takes into account that the median income is 42,000 based off of that I determined that any salary below 42,000 is "low earning" while anything above is "high earning"

based off the information above when the regression was ran I can answer this question by stating the following:

The introduction of the College Scorecard increased search activity on Google Trends for colleges with high-earning graduates by 0.2692 units relative to what it did for colleges with low-earning graduates, with a standard error of 0.4241. This result comes from the coefficients in my regression. The t-value associated with HighEarning is 0.6348, with a p-value of 0.5256, suggesting that the coefficient is not statistically significant. Similarly, for LowEarning, the t-value is 0.6051 with a p-value of 0.5451, indicating no statistical significance. The coefficient for monthly_date is -0.0026 with a standard error of 0.0003, and it is statistically significant (p-value \< 2.2e-16). The RMSE of the model is 1.19668, and the adjusted R-squared is 0.0181.

Holding everything constant a one unit increase in high earning is associated with a 0.2692 increase in the mean standard index. However, since our p-value of 0.5256, this suggests that this coefficient isn't statistically significant. We cannot determine if there is a relationship between high earning and mean standard index. This also holds true for low earning individuals which has a lower coefficient (.2567) and a higher P-value (0.5451). This leads me to believe that there is no correlation between the introduction of the college scorecard on high earning and low earning individuals.

\

```{r}

```

```{r}

```

```{r}

```

```{r}

```
